Multi-reference pangenome graphs

### 2022-01-08 manuscript/fig_induction.tex
vizual pruuf

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    font=\sffamily,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
    graphnode/.style={rectangle, draw=gray!60, fill=black!100, text=white, very thick, minimum size=5mm},
    keynode/.style={rectangle, draw=black!60, fill=gray!10, thick, minimum size=1mm}
]
%Nodes
\node[squarednode] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

\node[squarednode] (seqB1) [below of=seqA1] {G};
\node[squarednode] (seqB2) [right of=seqB1] {C};
\node[squarednode] (seqB3) [right of=seqB2] {T};
\node[squarednode] (seqB4) [right of=seqB3] {T};
\node[squarednode] (seqB5) [right of=seqB4] {A};
\node[squarednode] (seqB6) [right of=seqB5] {C};
\node[squarednode] (seqB7) [right of=seqB6] {G};

\node[squarednode] (seqC1) [below of=seqB1] {G};
\node[squarednode] (seqC2) [right of=seqC1] {A};
\node[squarednode] (seqC3) [right of=seqC2] {T};
\node[squarednode] (seqC4) [below of=seqB6] {C};
\node[squarednode] (seqC5) [right of=seqC4] {A};

@@

% alignments
\draw[very thick,color=gray!50] (seqA1) -- (seqB1);
\draw[very thick,color=gray!50] (seqA1) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC1);
%\draw[line width=1.0,color=gray!100] (seqA2) -- (seqB2);
\draw[very thick,color=gray!50] (seqA2) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC2);

@@

%\begin{scope}[node distance=1cm]
\node[graphnode] (g2) [below = 0.75cm of seqC2] {2};
\node[graphnode] (g1) [below = 1.25cm of seqC1] {1};
\node[graphnode] (g3) [below = 0.5cm of g2] {8};
\node[graphnode] (g4) [below = 1.25cm of seqC3] {3};
\node[graphnode] (g5) [right of=g4] {4};
\node[graphnode] (g6) [right of=g5] {5};
\node[graphnode] (g7) [below = 1.25cm of seqC4] {6};
\node[graphnode] (g8) [below = 0.75cm of seqC5] {7};
\node[graphnode] (g9) [below = 0.5cm of g8] {9};
%\end{scope}

\draw[line width=1.0] (g1) to (g2);
\draw[line width=1.0] (g1) to (g3);
\draw[line width=1.0] (g2) to (g4);
\draw[line width=1.0] (g3) to (g4);
\draw[line width=1.0] (g4) to (g5);
\draw[line width=1.0] (g4) to [looseness=1] (g7);
\draw[line width=1.0] (g5) to (g6);
\draw[line width=1.0] (g6) to (g7);
\draw[line width=1.0] (g7) to (g8);
\draw[line width=1.0] (g7) to (g9);

%\begin{pgfonlayer}{bg}    % select the background layer
\draw[very thick,color=red!100] (seqA1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[very thick,color=red!100] (seqB1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[very thick,color=red!100] (seqC1) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
%\draw[very thick,color=red!100,looseness=0.5] (seqB1.south) to (g1.north);
%\draw[very thick,color=red!100,looseness=0.5] (seqC1.south) to (g1.north);

\draw[very thick,color={rgb:red,1;orange,1}] (seqA2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);
\draw[very thick,color={rgb:red,1;orange,1}] (seqC2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);

\draw[very thick,color=orange!100] (seqA3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[very thick,color=orange!100] (seqB3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[very thick,color=orange!100] (seqC3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[very thick,color=green!100] (seqA4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
\draw[very thick,color=green!100] (seqB4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
%\draw[very thick,color=blue!100] (seqC3) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[very thick,color={rgb:blue,1;green,1}] (seqA5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);
\draw[very thick,color={rgb:blue,1;green,1}] (seqB5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);

\draw[very thick,color=blue!100] (seqA6) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[very thick,color=blue!100] (seqB6) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[very thick,color=blue!100] (seqC4) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);

\draw[very thick,color={rgb:blue,1;purple,1}] (seqA7) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);
\draw[very thick,color={rgb:blue,1;purple,1}] (seqC5) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);

\draw[very thick,color=purple!100] (seqB7) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g9);

\draw[very thick,color=brown] (seqB2) to [looseness=0.3,in=45,out=-45, edge node={node [sloped,above] {}}] (g3);

>>>>

\begin{document}
\begin{tikzpicture}[auto,
    node distance= 10mm and 20mm,
    font=\sffamily,
    roundnode/.style={circle, draw=black!60, fill=gray!10, very thick, minimum size=7mm},
    squarednode/.style={rectangle, draw=black!60, fill=gray!10, very thick, minimum size=5mm},
    graphnode/.style={rectangle, draw=gray!60, fill=black!100, text=white, very thick, minimum size=5mm},
    keynode/.style={rectangle, draw=black!60, fill=gray!10, thick, minimum size=1mm}
]
%Nodes
\node[squarednode,label=left:text1] (seqA1) {G};
\node[squarednode] (seqA2) [right of=seqA1] {A};
\node[squarednode] (seqA3) [right of=seqA2] {T};
\node[squarednode] (seqA4) [right of=seqA3] {T};
\node[squarednode] (seqA5) [right of=seqA4] {A};
\node[squarednode] (seqA6) [right of=seqA5] {C};
\node[squarednode] (seqA7) [right of=seqA6] {A};

\node[squarednode,label=left:text2] (seqB1) [below of=seqA1] {G};
\node[squarednode] (seqB2) [right of=seqB1] {C};
\node[squarednode] (seqB3) [right of=seqB2] {T};
\node[squarednode] (seqB4) [right of=seqB3] {T};
\node[squarednode] (seqB5) [right of=seqB4] {A};
\node[squarednode] (seqB6) [right of=seqB5] {C};
\node[squarednode] (seqB7) [right of=seqB6] {G};

\node[squarednode,label=left:text3] (seqC1) [below of=seqB1] {G};
\node[squarednode] (seqC2) [right of=seqC1] {A};
\node[squarednode] (seqC3) [right of=seqC2] {T};
\node[squarednode] (seqC4) [below of=seqB6] {C};
\node[squarednode] (seqC5) [right of=seqC4] {A};

@@

% alignments
\draw[very thick,color=gray!50] (seqA1) -- (seqB1);
%\draw[very thick,color=gray!50] (seqA1) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC1);
\draw[very thick,color=gray!50] (seqB1) -- (seqC1);

\draw[very thick,color=gray!50] (seqA2) to [in=135,out=225,looseness=0.5, edge node={node [sloped,above] {}}] (seqC2);

@@

%\begin{scope}[node distance=1cm]
\node[graphnode,draw={rgb:red,1;orange,1}] (g2) [below = 0.75cm of seqC2] {2};
\node[graphnode,draw=red!100,label=left:graph] (g1) [below = 1.25cm of seqC1] {1};
\node[graphnode,draw=brown] (g3) [below = 0.5cm of g2] {8};
\node[graphnode,draw=orange!100] (g4) [below = 1.25cm of seqC3] {3};
\node[graphnode,draw=green!100] (g5) [right of=g4] {4};
\node[graphnode,draw={rgb:blue,1;green,1}] (g6) [right of=g5] {5};
\node[graphnode,draw=blue!100] (g7) [below = 1.25cm of seqC4] {6};
\node[graphnode,draw={rgb:blue,1;purple,1}] (g8) [below = 0.75cm of seqC5] {7};
\node[graphnode,draw=purple!100] (g9) [below = 0.5cm of g8] {9};
%\end{scope}

\draw[very thick] (g1) to (g2);
\draw[very thick] (g1) to (g3);
\draw[very thick] (g2) to (g4);
\draw[very thick] (g3) to (g4);
\draw[very thick] (g4) to (g5);
\draw[very thick] (g4) to [looseness=1] (g7);
\draw[very thick] (g5) to (g6);
\draw[very thick] (g6) to (g7);
\draw[very thick] (g7) to (g8);
\draw[very thick] (g7) to (g9);

%\begin{pgfonlayer}{bg}    % select the background layer
\draw[very thick,color=red!100] (seqA1) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[very thick,color=red!100] (seqB1) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
\draw[very thick,color=red!100] (seqC1) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g1);
%\draw[very thick,color=red!100,looseness=0.5] (seqB1.south) to (g1.north);
%\draw[very thick,color=red!100,looseness=0.5] (seqC1.south) to (g1.north);

\draw[very thick,color={rgb:red,1;orange,1}] (seqA2) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);
\draw[very thick,color={rgb:red,1;orange,1}] (seqC2) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g2);

\draw[very thick,color=orange!100] (seqA3) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[very thick,color=orange!100] (seqB3) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);
\draw[very thick,color=orange!100] (seqC3) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[very thick,color=green!100] (seqA4) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
\draw[very thick,color=green!100] (seqB4) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g5);
%\draw[very thick,color=blue!100] (seqC3) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g4);

\draw[very thick,color={rgb:blue,1;green,1}] (seqA5) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);
\draw[very thick,color={rgb:blue,1;green,1}] (seqB5) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g6);

\draw[very thick,color=blue!100] (seqA6) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[very thick,color=blue!100] (seqB6) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);
\draw[very thick,color=blue!100] (seqC4) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g7);

\draw[very thick,color={rgb:blue,1;purple,1}] (seqA7) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);
\draw[very thick,color={rgb:blue,1;purple,1}] (seqC5) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g8);

\draw[very thick,color=purple!100] (seqB7) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g9);

\draw[very thick,color=brown] (seqB2) to [looseness=0.4,in=45,out=-45, edge node={node [sloped,above] {}}] (g3);
